NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-12-05 RefereeReply1.txt

We would like to thank the referee for his/her constructive and valuable 
comments.  The points raised clearly helped us to further improve the 
quality of the manuscript.  Below we give detailed replies to the referee's 
queries and indicate the corresponding adjustments or additions to the 
manuscript.  We thereby follow the referee's initial ordering: 
1) The use of alpha(0) is motivated by the real emission that takes place at
   q^2=0. In order to obtain pole cancellation between the reals and the virtuals
   we chose the same factor for the virtual contribution. We are aware that there
   are other valid choices, however, at least in this case, the differences are small
   compared to the genuine electroweak corrections. We added a corresponding sentence
   about the motivation of the choice to the draft.
2) Renormalization- and factorization scale have been varied indepedently from 1/2 to 2 within 
   a 7 point scale variation, i.e. the combinations 0.5/2 and 2/0.5 are not present. The scale
   uncertainty has then be determined by the envelope of the various results.
   We added this information to the draft.
3) We added a sentence stating this explicitly.
4) The only analysis for three or more photons (Ref 6) focusses on heavy intermediate BSM
   particles. Therefore it did not make sense to adopt this set of cuts and we rather used generic
   cuts similar to the one applied for diphoton searches (i.e. asymmetric cuts between 1st and
   2nd photon). But they are not according to a specific experimental analysis. Nevertheless 
   they have been chosen in such a way that they are likely to be similar/comparable to a possible
   experimental analysis.
5)
6)
7)
8)  The figure captions have been corrected.
9)  This has been rephrased to clearly state which particles the invariant 
    mass cut acts on.
10) The PDFs have been specified, and the respective publication referenced.
11) 
12) The description of the observables has been enhanced in the following 
    cases:
    - 
    - 
13) We agree and added a sentence stating exactly that.

### 2017-12-05 results.tex
worked on points 1-4 in referee report, added reference

In this section we present numerical results for the NLO QCD and NLO EW 
corrections to all three production processes of a diphoton pair in 
association with a third vector boson, a third photon, a $W$ or a $Z$ 
boson, at the LHC at a centre-of-mass energy of 13\,TeV. 
In case of an accompanying $W$ or a $Z$ boson, we consider the full 
off-shell leptonic final state, i.e.\ lepton-neutrino or lepton-pair 
production.
All results are obtained in the Standard Model using the complex-mass 
scheme \cite{Denner:2005fg} with the following input parameters
\begin{center}
  \begin{tabular}{rclrcl}
    $\alphazero$ &\shortequal& $1/137.03599976$  \qquad &&& \\
    $\Gmu$ &\shortequal& $1.1663787\times 10^{-5}\; \text{GeV}^2$ &&& \\
    $m_W$ &\shortequal& $80.385\; \text{GeV}$       & $\Gamma_W$ &\shortequal& $2.085\; \text{GeV}$ \\
    $m_Z$ &\shortequal& $91.1876\; \text{GeV}$      & $\Gamma_Z$ &\shortequal& $2.4952\; \text{GeV}$ \\
    $m_h$ &\shortequal& $125.0\; \text{GeV}$        & $\Gamma_h$ &\shortequal& $0$\\
    $m_t$ &\shortequal& $173.2\; \text{GeV}$        & $\Gamma_t$ &\shortequal& $0$\;.
  \end{tabular}
\end{center}
While we calculate triple photon production in the \alphazero-scheme, 
we use a mixed scheme for \aaw\ and \aaz production: at LO two 
powers of $\alpha$ are taken in the \alphazero-scheme, while 
one power of $\alpha$ is taken in the \Gmu-scheme. 
The additional power of $\alpha$ in the NLO EW correction 
is evaluated in \alphazero-scheme again.
The virtual amplitudes are renormalised correspondingly.
In all cases both the width of the top quark and the Higgs boson 
can safely be neglected as there are no diagrams containing either 
as $s$-channel propagators which can potentially go on-shell. 
All other lepton and parton masses and widths are set to zero, 
i.e.\ we are working in the five-flavour scheme.
We use the \textsc{CT14nlo} PDF set with $\alphas(m_Z)=0.118$ 
\cite{Dulat:2015mca}, interfaced through LHAPDF6 \cite{Buckley:2014ana}. 
The use of a QCD-only PDF is justified by the fact that, 
at LO, the photon induced corrections are either non-existent 
(\aaa, \aaw) or negligible (\aaz).
This finding will be detailed in Section \ref{sec:results:aaz}.

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  %\begin{split}
    \muR^0 = \muF^0 = %\left\{
    %\begin{array}{ll}
     % m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
      \tfrac{1}{2}\,H_T' \;. %& \text{in \aaw\ and \aaz\ production.}
    %\end{array}\right.
  %\end{split}
\end{equation}
In the case of the triple photon process $ H_\mathrm{T}' $ is just given by the scalar sum of all final state 
transverse momenta, for the two processes with the massive vector bosons it is defined as 
\begin{equation}
  \label{ew:defHT}
  \begin{split}
    H_\mathrm{T}' = E_\mathrm{T}^V + \sum_{\gamma,q,g} p_{\mathrm{T},i}
  \end{split}
\end{equation}
with $\left.E_\mathrm{T}^W\right.^2=(p_\ell+p_\nu)^2$ and 
$\left.E_\mathrm{T}^Z\right.^2=(p_{\ell^+}+p_{\ell^-})^2$ 
in full analogy to the case of the case of vector boson production 
in association with jets \cite{Berger:2009ep}.
As the Born process in each case has no $\muR$ dependence, we 
do not expect the choice of scale to have a significant influence 
on the size of the relative QCD and EW corrections.
We calculate the leading order cross section $\rd\sigma_\text{LO}(\muF)$, 
which only depends on the factorisation scale $\muF$, the 
NLO QCD differential correction factor $\deltaQCD(\muR,\muF)$, 
introducing the additional $\muR$-dependence, and the NLO EW 
differential correction factor $\deltaEW(\muF^0)$. 
To estimate the impact of yet-to-be-calculated higher-order 
corrections we vary the free scales $\muR$ and $\muF$ 
by the conventional factor of two around their central values 
$\muR^0$ and $\muF^0$, respectively.
We do not vary the factorisation scale for the determination 
of $\deltaEW$ as the inherent, albeit normally phenomenologically 
irrelevant, stabilisation of the $\muF$-dependence at NLO EW 
is not reflected in our chosen PDF.
Hence, our NLO EW result exhibits the exact same $\muF$-dependence 
as the LO result.
We define 
\begin{equation}
  \label{eq:defnlo}
  \begin{split}
    \rd\sigma_\text{NLO QCD}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\\
    \rd\sigma_\text{NLO EW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDpEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDtEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\left(1+\deltaEW\right)\;.
  \end{split}
\end{equation}
Therein, the difference between NLO \QCDpEW\ and NLO \QCDtEW, which 
is of relative $\order(\alphas\alpha)$, can serve as an indicator 
of the potential size of unknown corrections at that order.

>>>>

In this section we present numerical results for the NLO QCD and NLO EW 
corrections to all three production processes of a diphoton pair in 
association with a third vector boson, a third photon, a $W$ or a $Z$ 
boson, at the LHC at a centre-of-mass energy of 13\,TeV. 
In case of an accompanying $W$ or a $Z$ boson, we consider the full 
off-shell leptonic final state, i.e.\ lepton-neutrino or lepton-pair 
production.
All results are obtained in the Standard Model using the complex-mass 
scheme \cite{Denner:2005fg} with the following input parameters
\begin{center}
  \begin{tabular}{rclrcl}
    $\alphazero$ &\shortequal& $1/137.03599976$  \qquad &&& \\
    $\Gmu$ &\shortequal& $1.1663787\times 10^{-5}\; \text{GeV}^2$ &&& \\
    $m_W$ &\shortequal& $80.385\; \text{GeV}$       & $\Gamma_W$ &\shortequal& $2.085\; \text{GeV}$ \\
    $m_Z$ &\shortequal& $91.1876\; \text{GeV}$      & $\Gamma_Z$ &\shortequal& $2.4952\; \text{GeV}$ \\
    $m_h$ &\shortequal& $125.0\; \text{GeV}$        & $\Gamma_h$ &\shortequal& $0$\\
    $m_t$ &\shortequal& $173.2\; \text{GeV}$        & $\Gamma_t$ &\shortequal& $0$\;.
  \end{tabular}
\end{center}
While we calculate triple photon production in the \alphazero-scheme, 
we use a mixed scheme for \aaw\ and \aaz production: at LO two 
powers of $\alpha$ are taken in the \alphazero-scheme, while 
one power of $\alpha$ is taken in the \Gmu-scheme. 
The additional power of $\alpha$ in the NLO EW correction 
is evaluated in \alphazero-scheme again. \revised{This choice is motivated by the fact
that the real emission contribution takes place at $q^2=0$ and in order to obtain
pole cancellation between the real emission contribution and the virtual corrections we
chose the same factors in both contributions. An alternative choice would be to use
the \Gmu-scheme throughout.}
The virtual amplitudes are renormalised correspondingly.
In all cases both the width of the top quark and the Higgs boson 
can safely be neglected as there are no diagrams containing either 
as $s$-channel propagators which can potentially go on-shell. 
All other lepton and parton masses and widths are set to zero, 
i.e.\ we are working in the five-flavour scheme.
We use the \textsc{CT14nlo} PDF set with $\alphas(m_Z)=0.118$ 
\cite{Dulat:2015mca}, interfaced through LHAPDF6 \cite{Buckley:2014ana}. 
The use of a QCD-only PDF is justified by the fact that, 
at LO, the photon induced corrections are either non-existent 
(\aaa, \aaw) or negligible (\aaz).
This finding will be detailed in Section \ref{sec:results:aaz}.

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  %\begin{split}
    \muR^0 = \muF^0 = %\left\{
    %\begin{array}{ll}
     % m_{\aaa} \qquad & \text{in \aaa\ production} \\[2mm]
      \tfrac{1}{2}\,H_T' \;. %& \text{in \aaw\ and \aaz\ production.}
    %\end{array}\right.
  %\end{split}
\end{equation}
In the case of the triple photon process $ H_\mathrm{T}' $ is just given by the scalar sum of all final state 
transverse momenta, for the two processes with the massive vector bosons it is defined as 
\begin{equation}
  \label{ew:defHT}
  \begin{split}
    H_\mathrm{T}' = E_\mathrm{T}^V + \sum_{\gamma,q,g} p_{\mathrm{T},i}
  \end{split}
\end{equation}
with $\left.E_\mathrm{T}^W\right.^2=(p_\ell+p_\nu)^2$ and 
$\left.E_\mathrm{T}^Z\right.^2=(p_{\ell^+}+p_{\ell^-})^2$ 
in full analogy to the case of the case of vector boson production 
in association with jets \cite{Berger:2009ep}.
As the Born process in each case has no $\muR$ dependence, we 
do not expect the choice of scale to have a significant influence 
on the size of the relative QCD and EW corrections.
We calculate the leading order cross section $\rd\sigma_\text{LO}(\muF)$, 
which only depends on the factorisation scale $\muF$, the 
NLO QCD differential correction factor $\deltaQCD(\muR,\muF)$, 
introducing the additional $\muR$-dependence, and the NLO EW 
differential correction factor $\deltaEW(\muF^0)$. 
To estimate the impact of yet-to-be-calculated higher-order 
corrections we vary the free scales $\muR$ and $\muF$ 
by the conventional factor of two around their central values 
$\muR^0$ and $\muF^0$, respectively. \revised{ $\muR$ and $\muF$ are
varied independently within a 7-point scale variation, i.e. the 
two cases where one scale is the inverse of the other scale is not present.
The uncertainty bands shown later in the various distributions are given
by the envelope of these 7 results. It should be noted that the QCD scale variation is
completely unrelated to the electroweak corrections. Nevertheless it is interesting
to compare the two as it is the general assumption the the LO QCD scale uncertainty
covers all higher order effect. Therefore it is interesting and important to investigate
whether this assumption is true. }
We do not vary the factorisation scale for the determination 
of $\deltaEW$ as the inherent, albeit normally phenomenologically 
irrelevant, stabilisation of the $\muF$-dependence at NLO EW 
is not reflected in our chosen PDF.
Hence, our NLO EW result exhibits the exact same $\muF$-dependence 
as the LO result.
We define 
\begin{equation}
  \label{eq:defnlo}
  \begin{split}
    \rd\sigma_\text{NLO QCD}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\\
    \rd\sigma_\text{NLO EW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDpEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD+\deltaEW\right)\\
    \rd\sigma_\text{NLO \QCDtEW}
    \,=\;&\rd\sigma_\text{LO}\left(1+\deltaQCD\right)\left(1+\deltaEW\right)\;.
  \end{split}
\end{equation}
Therein, the difference between NLO \QCDpEW\ and NLO \QCDtEW, which 
is of relative $\order(\alphas\alpha)$, can serve as an indicator 
of the potential size of unknown corrections at that order.

### 2017-12-05 setup.tex
worked on points 1-4 in referee report, added reference

This combination of tools was previously used to calculate the 
NLO QCD corrections to $ZZ+\text{jet}$, $t\bar{t}+0,1\,\text{jets}$, 
$W^{+}W^{-}b\bar{b}$ and $h+0,1,2,3\,\text{jets}$ production 
in \cite{Binoth:2009wk,Hoeche:2013mua,Heinrich:2013qaa,
  Greiner:2015jha,Greiner:2016awe,Heinrich:2017bqp} and the 
NLO EW corrections to $\gamma\gamma+0,1,2\,\text{jets}$ production 
in \cite{Chiesa:2017gqx}.

>>>>

This combination of tools was previously used to calculate the 
NLO QCD corrections to $ZZ+\text{jet}$, $t\bar{t}+0,1\,\text{jets}$, 
$W^{+}W^{-}b\bar{b}$, $h+0,1,2,3\,\text{jets}$  and $\gamma\gamma b \bar{b}$ production 
in \cite{Binoth:2009wk,Hoeche:2013mua,Heinrich:2013qaa,
  Greiner:2015jha,Greiner:2016awe,Heinrich:2017bqp,Faeh:2017fpp} and the 
NLO EW corrections to $\gamma\gamma+0,1,2\,\text{jets}$ production 
in \cite{Chiesa:2017gqx}.
